PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2015-03-11 qfenv_paper/hahn_qfenv_abstract.tex
minor changes

\documentclass[manuscript]{aastex}
\bibliographystyle{apj}

@@

%internal short cuts
\def \lowenvthresh {0.5}
\def \highenvthresh {3.0}
\def \apradius{2.5}
\def \apheight{35}

@@

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
John~Moustakas\altaffilmark{2},
Alison L.~Coil\altaffilmark{3}, 
Richard J.~Cool\altaffilmark{4}, 
Daniel J.~Eisenstein\altaffilmark{5},
Ramin A.~Skibba\altaffilmark{3}
Kenneth C.~Wong\altaffilmark{6}, 
Guangtun~Zhu\altaffilmark{7,8}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Hubble Fellow; Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\mathrm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
14,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population. For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\mathrm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

\keywords{cosmology:observations --- galaxies: evolution --- galaxies:groups --- galaxies: star formation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their surroundings, with a strong dependence of the quiescent fraction of galaxies on their local environment (e.g. \citealt{hubble36a, oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see \citealt{blanton09a}).  The strength of this dependence is itself a strongly decreasing function of galaxy stellar mass; at the extreme, the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their star formation only in dense regions, and never in isolation (\citealt{geha12a}). These effects also vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field, found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}). Clearly understanding the properties of galaxies in the present-day universe requires a careful investigation of the role of environment, and how that role changes over time.

%Moreover, at $z < 1$ lower star-formation rate early-type galaxies are found populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).

Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted within the context of the evolving galaxy population. For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmental effects are unlikely to cause the overall star-formation rate decline.

During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). \cite{Moustakas:2013aa}, for instance, find that since $z \sim 1.0$ the $\sim 50\%$ decline in the number density of massive star-forming galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$) is complemented by the rise in number density of intermediate-mass quiescent galaxies ($\mathcal{M}_{*} \approx 10^{9.5} - 10^{10}\mathcal{M}_{\odot}$), by a factor of $ 2-3$, and massive quiescent galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$ ), by $\sim 20\%$. On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}). These changes in galaxy population are likely a result of physical processes that cause the cessation of star-formation in star-forming galaxies.

Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppresses the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}). Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation.

Observations such as \cite{Weinmann:2006aa} and \cite{Peng:2010aa} credit some of these proposed internal processes for the cessation of star-formation, especially in massive galaxies. Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein). However, it remains to be determined whether the environmental trends in galaxy properties reflect the direct effect of external environment on the galaxies' evolution (e.g. ram pressure, tidal forces, mergers) or reflect statistical differences in the histories of galaxies in different environments (e.g. an earlier formation time in dense regions).

In this paper we take the most straightforward investigation
by directly determining the star-forming properties of galaxies
as a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
end their star formation over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the PRIism MUlti-object Survey (PRIMUS; \citealt{Coil:2011aa},
\citealt{Cool:2013aa}), the largest available redshift survey covering
the epochs between $0<z<1$.

In Section \ref{sec:sample} we present a brief description of the
PRIMUS and SDSS data, our mass complete sample construction, and
galaxy environment measurements. After dividing our galaxy sample into
subsamples of star-forming or quiescent and high or low density
environments, we compute and examine the evolution of the stellar mass
functions for our subsamples in Section \ref{sec:smf}. In
Section \ref{sec:qf_const}, we calculate the quiescent fraction,
analyze the evolution of the quiescent fraction, quantify the effects
of environment on the quiescent fraction evolution, and discuss the
implications of our quiescent fraction results on the cessation of
star-formation in galaxies. Finally in Section \ref{sec:summary} we
summarize our results.

Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \mathrm{km} \; \mathrm{s}^{-1}
\mathrm{Mpc}^{-1}$. All magnitudes are AB-relative.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on
the evolution of the quiescent fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to robustly measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\citealt{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
brief summary of the PRIMUS and SDSS data used for our sample
selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
Then, in Section \ref{sec:sfq}, we classify the sample galaxies as quiescent or star-forming. 
We calculate the environment
using a volume-limited Environment Defining Population in Section
\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
account for edge effects in the surveys.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \mathrm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \mathrm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields. Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDSS-GALEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and $ugriz$ photometry from the SDSS Data Release 7 (DR7; \citealt{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\citealt{Blanton:2005aa}). We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \mathrm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FUV photometry for the SDSS-{\em GALEX} galaxies. For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude. These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \mathrm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}. As previously done on the PRIMUS data in Section \ref{sec:primus}, we use \texttt{iSEDfit} to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.

The SDSS-{\em GALEX} data discussed above is derived from the NYU-VAGC
based on SDSS Data Release 7, using the standard SDSS photometric
measurements. Several investigators have found that the background
subtraction techniques used in the standard photometric catalogs
introduce a size dependent bias in the galaxy fluxes and consequently
stellar masses (\citealt{West:2005aa, Blanton:2005ab, Lauer:2007aa, Bernardi:2007aa,
  Hyde:2009aa, West:2010aa}).

In order to quantify the effects of these photometric underestimations
in our analysis, we tried replacing our SDSS fluxes in the $ugriz$
band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog,
which incorporate the improved background subtraction presented in
\cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the
standard SDSS \texttt{cmodel} fluxes. Using the ratio of the
luminosity derived from the improved photometry over the luminosity
derived from the standard NYU-VAGC photometry, we apply a preliminary
correction to the stellar mass values obtained from \texttt{iSEDfit}
assuming a consistent mass-to-light ratio. This mass correction leads
to a significant increase in the stellar mass function for
$\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of
the mass correction was negligible for the quiescent fraction
evolution results. As a result, for the results presented here we use
the standard SDSS fluxes and we do not discuss the issues with
photometric measurements any further in this paper. We note that a
thorough investigation of these issues to understand their effect on
the stellar mass function requires a reanalysis of both the SDSS
photometry and the deeper photometry used for PRIMUS targeting.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:target} 
From the low redshift SDSS-{\em GALEX} and intermediate redshift
PRIMUS data we define our mass complete galaxy
sample. We begin by imposing the parent sample selection criteria from
\cite{Moustakas:2013aa}. More specifically, we take the statistically
complete {\em primary} sample from the PRIMUS data
(\citealt{Coil:2011aa}) and impose magnitude limits on optical
selection bands as specified in \cite{Moustakas:2013aa} Table 1. These
limits are in different optical selection bands and have distinct
values for the five PRIMUS target fields. We then exclude stars and
broad-line AGN to only select objects spectroscopically classified as
galaxies, with high-quality spectroscopic redshifts ($Q \geq
3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the
PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations
from sample variance and $ z < 0.8$ is selected due to the lack of
sufficient statistics in subsamples defined below.

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\mathrm{target}} \times f_{\mathrm{collision}} \times f_{\mathrm{success}})^{-1},
\end{equation}
as in Equation (1) in \cite{Moustakas:2013aa}.

Since we are ultimately interested in a mass complete galaxy sample to
derive SMFs and QFs, next we impose stellar mass completeness limits
to our galaxy sample.
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\mathrm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\mathrm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\mathrm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\mathrm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

For the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.05 < z < 0.12$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}). To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog. Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio completeness limit of the SDSS-{\em GALEX} data within the imposed redshift limits (\citealt{Blanton:2005ab, Baldry:2008aa, Moustakas:2013aa}). We then apply this mass limit in order to obtain our mass-complete galaxy sample at low redshift.

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Williams:2009aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation} \label{eq:qsfclass} 
\mathrm{log}(\mathrm{SFR}_{\mathrm{min}}) = -0.49 + 0.64 \mathrm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY ENVIRONMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it. We use fixed aperture measurements in order to quantify galaxy environment with an aperture sufficiently large to encompass massive halos (\citealt{Muldrew:2012aa, Skibba:2013aa}).
%We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
\apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

Before we measure the environment for our galaxy sample, we first
construct a volume limited Environment Defining Population (EDP) with
absolute magnitude cut-offs ($M_{r}$) in redshift bins with $\Delta z
\sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the
cumulative number density over $M_{r}$ for all redshift bins are
equal.  We make this choice in order to construct an EDP that contains
similar galaxy populations through the redshift range (i.e. accounts
for the progenitor bias). In their analysis of this method,
\cite{Behroozi:2013aa} and \cite{Leja:2013aa} find that although it
does not precisely account for the scatter in mass accretion or
galaxy-galaxy mergers, it provides a reasonable means to compare
galaxy populations over a wide range of cosmic time.

In constructing the PRIMUS EDP we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}). We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($z = 0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\mathrm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\mathrm{lim}}$ have fewer galaxies than the bin at $M_{r, \mathrm{lim}}$. We conservatively choose $M_{r, \mathrm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.97$. Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\mathrm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin with $M_{r, \mathrm{lim}}(0.6 < z < 0.8) = -20.97$.

For the SDSS EDP, we do not use the SDSS-{\em GALEX} parent data,
which is limited to the combined angular selection window of the
VAGC and {\em GALEX} (Section \ref{sec:sdss}). Instead, since FUV, NUV
values are not necessary for the EDP, we extend the parent data of the
SDSS EDP to the entire NYU-VAGC, including galaxies outside of the
{\em GALEX} window function. Furthermore, we impose a redshift range
of $0.05-0.12$ on the SDSS EDP. This redshift range was determined to
account for the lack of faint galaxies at $z \sim 0.2$ and the lack of
bright galaxies at $z \sim 0.01$ in the VAGC. As with the PRIMUS
redshift bins, we determine the SDSS EDP $M_{r, \mathrm{lim}}$ by matching
the cumulative number density of the highest redshift bin. For
redshift bins $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
$M_{r,\mathrm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
respectively. These absolute magnitude limits are illustrated in
Figure \ref{fig:targetEDP}, where we present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) ad the EDP (red circles). 
The left-most panel corresponds to the samples derived from the SDSS-{\em GALEX} data while the rest correspond to samples derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
Figure \ref{fig:targetEDP} shows clear $M_r$ cutoffs in the
$M_{r}$ distribution versus redshift for the EDP on top
of our galaxy sample.

For our SDSS-{\em GALEX} galaxy sample, in Section \ref{sec:target}, we apply PRIMUS redshift errors in order to establish a consistent measurement of environment throughout our redshift range. We appropriately apply equivalent redshift adjustments for the SDSS EDP. For the SDSS EDP galaxies that are also contained within the SDSS-{\em GALEX} sample, we adjust the redshift by an identical amount. For the rest, we apply the same redshift adjustment procedure described in Section \ref{sec:target} in order to obtain PRIMUS level redshift uncertainties.

>>>>

\documentclass{emulateapj}
\bibliographystyle{apj}

@@

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \Hbp {H$\beta ^\prime$}
\def \lowenvthresh {0.5}
\def \highenvthresh {3.0}
\def \apradius{2.5}
\def \apheight{35}

@@

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
John~Moustakas\altaffilmark{2},
Alison L.~Coil\altaffilmark{3}, 
Richard J.~Cool\altaffilmark{4}, 
Daniel J.~Eisenstein\altaffilmark{5},
Ramin A.~Skibba\altaffilmark{3}
Kenneth C.~Wong\altaffilmark{6}, 
Guangtun~Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Hubble Fellow; Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\mathrm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
14,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population. For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\mathrm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}
\section*{}
\end{document}
